### 2014-09-17 drafts/ApproximatePCFG/ApproximatePCFG.tex
Added log untracked files for Approximate inference and stochastic rewrite system (SRS).

@@

@@

Suppose, by contradiction, that their is some linear combination $a_1,
..., a_K$ such that $(1-\Phi^\ell) a = 0$. This implies that each $a_i
= \sum_{j} \Phi^\ell_{i, j} a_j$. Recall that the element of
$\Phi^\ell_{A, B} = \sum_{A \rightarrow B C} \p(A \rightarrow B C)$,
where $A$ and $B$ are nonterminals. For the PCFG defined by these
probabilities to be valid, $\Phi^\ell_{A,B}$ must be less than
one. Otherwise, there would be a nonzero probability of an infinite
string. Taking the absolute values of both sides of the equation
above, we see that $|{a_i}| \leq \sum_{j} \Phi^\ell_{i, j} |
a_j|$. But if this is true, then  TODO

>>>>

\usepackage{graphicx}

@@

\subsection{A serious problem with boundary probabilities}
Unfortunately, there is are serious problems with using boundary
probabilities. First, the dependency between the first and last word
of a constituent decreases rapidly with the length of the
constitutent. Second, since calculating the boundary probability
involves taking the expectation over yields of all lengths, the value
assigned does not take into accoutn the length of the constitutent,
and produces values that upper bound the insid probability of a
consituent even for two word constitutent. But even an unlikely pair
of adjacent words is going to have a higher probability than a typical
long sentence. Therefore, we need to come up with a scoring function
that takes into account the length of the constitutent.

\section{Using constituent length to upper bound inside probabilities}
The probability that symbol $A$ yields any constitutent of length $n$
is greater than or equal to the probability that symbol $A$ yields any
specific string of words of that length.

Let $\lambda(A, n) \triangleq p(A \text{ yields a string of lengths }
n)$. This probability can be calculated recursively: 
\begin{align}
\lambda(A, n=1) =& \sum_{A \leftarrow t} \psi(A \leftarrow t)\\ 
\lambda(A, n>1) =& \sum_{A \leftarrow B \,C} \sum_{k=1}^{n-1} \psi(A \leftarrow B\, C) 
  \lambda(B, k) \lambda(C, k=1)\\ 
\end{align}

This recursive definition leads directly to an $O(Kn^2)$ algorithm for
$\lambda$.

\begin{figure}
\begin{minipage}[t]{\textwidth}
  \includegraphics[width=\linewidth]{figures/toy_grammar_approx_vs_exact.pdf}
\end{minipage}
\begin{minipage}[t]{4cm}
  \begin{align*}
    S \rightarrow& \,L\, S :: 0.1 \, | \,a :: 0.9\\
    L \rightarrow& \,L\, S :: 0.0001\, | \, a :: 0.999\\
  \end{align*}
  \centering (a)\par
\end{minipage}

\begin{minipage}[t]{\textwidth}
  \caption{A comparison of the approximate and exact ``Inside''
    algorithms on the toy grammar (c). (a) The number of edges seen by
    the algorithm. The exact Inside algorithm has a predictable $n^3$
    behavior because it looks once at every edge $(A, i, k, j)$. The
    approximate algorithm ignores edges that are gauranteed to be
    insignificant, so that the number of inspected edges is
    dramatically reduced. (b) The amount by which the approximate
    Inside algorithm over estimates the loglikelihood of the
    sentence. }
\end{minipage}
\end{figure}

@@

Suppose, by contradiction, that their is some linear combination $a_1,
..., a_K$ such that $(1-\Phi^\ell) a = 0$. This implies that each $a_i
= \sum_{j} \Phi^\ell_{i, j} a_j$. Recall that the element of
$\Phi^\ell_{A, B} = \sum_{A \rightarrow B C} p(A \rightarrow B C)$,
where $A$ and $B$ are nonterminals. For the PCFG defined by these
probabilities to be valid, $\Phi^\ell_{A,B}$ must be less than
one. Otherwise, there would be a nonzero probability of an infinite
string. Taking the absolute values of both sides of the equation
above, we see that $|{a_i}| \leq \sum_{j} \Phi^\ell_{i, j} |
a_j|$. But if this is true, then  TODO
